---
title: "Twitter Account Report"
author: "tweetDisect"
output: word_document
params:
  username : username
  waffle : waffle
  ts : ts
  tweets : tweets
  top15 : top15
  emotions: emotions
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
For ``r params$username``.This report will focus on three types of analysis. Account data analysis, Frequency analysis & Content analysis. The data was pulled from [twitter.com](www.twitter.com). This twitter API retrieves only public data that  ``r params$username`` chose to share with the world. So without further to do let's get stated!

## 1) Account data analysis
Here we will focus on the relationships ``r params$username`` forms with other twitter users. Specifically we will observe the mutual/disaprate relationships ratio. From the people who ``r params$username`` follows how many do follow him back? The next waffle chart will display the difference in proprtions.
```{r, echo=FALSE}
params$waffle
```

## 2) Frequency analysis
For this section we will observe together how frequent does ``r params$username`` tweets? And what does he/she usally tweets about. First, we will display a time series of the amount of tweets tweeted by ``r params$username``
```{r, echo=FALSE}
params$ts
```
After a simple word count performed on the tweets data, we were able to identify the most tweeted 15 words excluding stop words like helping verbs, the/a/an. Those words are mostly recognized entities that ``r params$username`` usually tweets about.
```{r, echo=FALSE}
params$top15
```
And here are the latest three tweets.
```{r,echo=FALSE}
params$tweets
```

## 3) Content analysis
The final section might be a little personal. We will take a look on the proportions of different emotions ``r params$username`` tweets convey. The next plot displays the mixture of trust, anticipation, joy, sadness, fear, surprise, anger & disgust. These information are obtained via a technique called Sentiment Analysis.
```{r, echo=FALSE}
params$emotions
```
If the pattern observed isn't really ideal, you can talk him/her on twitter @``r params$username``. We hope that you enjoyed reading this report & found it informative. See you in further analysis at [tweetDisect](https://muhammadezzat.shinyapps.io/tweetDisect/). Goodbye!



